---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.width = 9,
  fig.height = 10,
  cache = TRUE
)
```

# ggcompoplot

The goal of ggcompoplot is to create compoplots that can be manipulated using
the grammar of graphics. This code originally appeared in 
https://zenodo.org/record/13007. 

## Installation

To install, download devtools, and copy and past this into your R console:

```{r, eval = FALSE}
devtools::install_github("zkamvar/ggcompoplot")
```


## Example

### Compoplot from DAPC Analysis (from adegenet)

```{r setup_adegenet, fig.width = 7, fig.height = 5}
library('adegenet')
library('ggcompoplot')
library('ggplot2')

data(microbov)
strata(microbov) <- data.frame(other(microbov))

dapc1 <- dapc(microbov, n.pca=20, n.da=15)

compoplot(dapc1, lab="") # Adegenet compoplot
```


### Using ggcompoplot

To use ggcompoplot, all you need is the results of your DAPC analysis and your
genind/genlight object:

```{r, ggcompoplot}
# Setting a named palette of colors
(rainbov <- setNames(rainbow(nPop(microbov)), popNames(microbov)))

ggcompoplot(dapc1, microbov, pal = rainbov) + theme(axis.text.x = element_blank())

# 3 columns
ggcompoplot(dapc1, microbov, cols = 3, pal = rainbov) + theme(axis.text.x = element_blank())

# Different color palette
ggcompoplot(dapc1, microbov, cols = 3, pal = funky) + theme(axis.text.x = element_blank())

# Per Country
setPop(microbov) <- ~coun
ggcompoplot(dapc1, microbov, pal = rainbov) + theme(axis.text.x = element_blank())
```

